The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-29 exp-resurgence.tex
Move section on 1-Gevrey series to "Bridging the gap"
Start revising it too.

\textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$. Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.}
\begin{lemma}%%\label{translation}
Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
    \label{change-chart}
    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.

@@

 \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & \textcolor{magenta}{e^{bz}}\,\mathcal{O}_{T^*B}(H)\\
& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  

@@

commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
\begin{lemma}%%\label{translation}
Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
    \label{change-chart}
    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
 \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
With a change of variable in the integral that defines the Laplace transform, we see that
\laplace_{\zeta, b} \varphi & = \int_{\mathcal{J}_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\mathcal{J}_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
& = e^{-b z} \int_{\mathcal{J}_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
& = e^{-b z} \laplace_{\zeta_b, 0} \varphi.
We now consider a rescale of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. 
Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and for some $\Lambda>0$, then
    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
    From the computation 
\laplace_{\xi, 0} \varphi & = \int_{\mathcal{J}_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\mathcal{J}_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
we get the desired result. 
%Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
\subsection{Analysis of the Laplace transform}\label{sec:laplace_analytic}
\subsubsection{Regularity and decay properties}\label{sec:reg-decay}
\textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}. Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$. In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$. When $\sigma>-1$, the singularity at $\zeta = \beta$ is integrable. Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.

\color{NavyBlue}
Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$. Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space. \textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.}
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $f \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta f| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta f$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta f$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $f$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta f$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta f| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that this bound on the Laplace transform of $f$ is itself a Laplace transform:
\[ |\laplace_{\zeta_\alpha, 0}^\theta f| \le \Gamma(\sigma) \Delta^{-\sigma} \|f\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta f\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|f\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}
Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. Choose any $\lambda' > \Lambda$. Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left. Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. Along $\mathcal{C}$, we have
\[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\mathcal{C}}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]

The inverse Laplace transform is given by the formula
\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\mathcal{C}}} e^{z\zeta_\alpha} \Phi\,dz. \]
When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
\begin{align*}
\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\mathcal{C}}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
\end{align*}
which we can rewrite as
\begin{align*}
\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
& \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
\end{align*}
using the new parameter $s = \sin(\varepsilon/2)\,t$. Recognizing the integral in the last line as itself a Laplace transform, we have
\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
which is what we wanted to show.

>>>>

\textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$. Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_\alpha B$, is compatible with $\laplace_{\zeta, \alpha}$.}
\begin{lemma}\label{translation}
If the Laplace transform of $\varphi$ is well-defined, then

Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
   \begin{equation}
    \label{change-chart}
    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
\end{equation}
\begin{todo}
In other words, the diagram
\begin{center}
\begin{tikzcd}[row sep=12mm, column sep=2mm]
\mathcal{O}(T^*B) \arrow[rr, "e^{\alpha z}"] & & \mathcal{O}(T^*B)\\
& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_\alpha, 0}"]\arrow[ur,swap,"\laplace_{\zeta, \alpha}"]
\end{tikzcd}
\end{center}
commutes, where $H$ is the half-plane $\Re(z) > 0$.
\end{todo}
\end{lemma}
\color{black}
\color{RoyalBlue}
\begin{lemma}%%\label{translation}
Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
   \begin{equation}
    \label{change-chart}
    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
\end{equation}
In other words, the diagram
\begin{center}
\begin{tikzcd}
 \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
\end{tikzcd}
\end{center}
commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
\end{lemma}
\color{black}
\begin{proof}
With a change of variable in the integral that defines the Laplace transform, we see that
\begin{align*}
\laplace_{\zeta, b} \varphi & = \int_{\mathcal{J}_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\mathcal{J}_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
& = e^{-b z} \int_{\mathcal{J}_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
& = e^{-b z} \laplace_{\zeta_b, 0} \varphi.
\end{align*}
\end{proof}
We now consider a rescale of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. 
\begin{lemma}
Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and for some $\Lambda>0$, then
    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
\end{lemma}
\begin{proof}
    From the computation 
    \begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\mathcal{J}_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\mathcal{J}_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we get the desired result. 
\end{proof}
%
%Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
\subsection{Analysis of the Laplace transform}\label{sec:laplace_analytic}
%
\subsubsection{Regularity and decay properties}\label{sec:reg-decay}
%
\textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}. Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$. In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$. When $\sigma>-1$, the singularity at $\zeta = \beta$ is integrable. Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.

\color{NavyBlue}
Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$. Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space. \textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.} \textcolor{orange}{Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.}
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}
Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. Choose any $\lambda' > \Lambda$. Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left. Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. Along $\mathcal{C}$, we have
\[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]

The inverse Laplace transform is given by the formula
\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz. \]
When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
which we can rewrite as
\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
& \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
using the new parameter $s = \sin(\varepsilon/2)\,t$. Recognizing the integral in the last line as a Laplace transform integral, with the roles of position and frequency played by $s$ and $|\zeta_\alpha|$ respectively, we have
\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
which is what we wanted to show.
\textcolor{magenta}{[Introduce bare $\widehat{\Omega}$]}
\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
Here, we are thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}. We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate. This formal inverse is called the {\em Borel transform}. To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials 

@@

 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}

@@

and it extends to formal power series by countable linearity:
\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
This definition extends straightforwardly to fractional powers of $z$. Observing that   
\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
for every $\rho \in \R \setminus \Z_{\leq 0}$, we define 
\borel_\zeta[z^{-\rho-1}] \defeq \frac{\zeta^{\rho}}{\Gamma(\rho+1)}.
Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
